\documentclass[9pt]{extarticle}
\usepackage{fullpage}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{blindtext}
\usepackage{scrextend}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{float}

\input{../texcommon/commands.tex}

\begin{document}
\begin{table}
\centering{}
\begin{tabularx}{\textwidth}{lXlr}\\
\textbf{\huge{Ignacio Utrilla de Noriega}}&&&\\\cline{1-4}
& & & \\
&        &    Address:          &   Calle Lira 1, 2F, Sevilla 41003\\
&        &    DOB:              &   01/06/1990\\
&        &    Languages Spoken: &   Spanish, English\\
&        &    Email:            &   \href{mailto:ignacioutrilla@gmx.com}{ignacioutrilla@gmx.com}    \\
&        &    Phone:            &   +34 717716676\\
% &        &                      &   \\
\end{tabularx}
\end{table}

\textbf{Technical Skills and areas of expertise}\\\linea
\begin{itemize}
    \item{Zigbee, NFC Mifare, RFID, I2C, SPI, UART, Ethernet, Bluetooth, CANbus, RF}
    \item{C, Linux, C++, GIT, JIRA, SVN, \LaTeX}
    \item{ARM, ESP32, PIC32, PIC16, RPi}
    \item{Access control, Fire alarms, Ultra Low Power design, Biometrics, Radio certification, wearables, BMS}
    \item{ALTIUM Designer, KICAD, integrated circuits, PCB design, DFM, PCB testing, FreeCAD}
\end{itemize}
\vspace{1cm}

\textbf{Work Experience}\\\linea
\vspace{1cm}
\begin{table}[H]
\begin{tabularx}{\textwidth}{lcXr}
\textbf{\href{http://www.woodswallow.tech/}{Woodswallow}} & \emph{Sevilla (Sept 2019 to present)} & & \textbf{Team leader Firmware engineer}
\end{tabularx}
\end{table}
\par
\hspace{20pt} Developing and maintaining firmware for a communications hub (zigbee to proprietary radio link router) for the smart metering industry in the UK.
\begin{itemize}
    \item{\textbf{Technologies:} C, Zigbee, FreeRTOS, ARM, NXP LPC, Python}
    \item{\textbf{Key Duties Achievements:}}
\\$\cdot$ Leading a team which is now a reference for both the company and the client.
\\$\cdot$ Having reached a higher level of understanding of the project allowing me to foresee potential issues.
\\$\cdot$ Catching up in a very short period of time over a highly complex environment.
\\$\cdot$ Various successful enrollment of new developers into the project. 
\end{itemize}

\begin{table}[H]
\begin{tabularx}{\textwidth}{lcXr}
\textbf{\href{http://www.themobileknoledge.com/}{MobileKnowledge}} & \emph{Barcelona (July 2018 to July 2019)} & & \textbf{Firmware Engineer}
\end{tabularx}
\end{table}
\par
\hspace{20pt} Firmware development and integration of third party peripheral and sensor libraries to 
Cortex MCUs. As a part of a bigger team, my tasks are split into firmware development and support in 
different areas related with hardware and manufacture design. I also worked in potential customer project
definitions developing technical proposals along with the sales team.
\begin{itemize}
    \item{\textbf{Technologies:} C, RFID, NFC, wearables, ARM, Nordic, SPI, I2C, QT3d}
    \item{\textbf{Key Duties Achievements:}}
\\$\cdot$ Embedded RTOS port for STM32 Nucleo board.\emph{(Mynewt OS)}
\\$\cdot$ Firmware development for highly integrated low power devices.
\\$\cdot$ Project proposal technical definition and support for sales.
\\$\cdot$ Linux leading support.
\end{itemize}

\par
\begin{table}[H]
\begin{tabularx}{\textwidth}{lcXr}
\textbf{\href{http://www.biositesystems.com/}{Biosite Systems}} & \emph{Birmingham (March 2016 to March 2018)} & & \textbf{Firmware and electronic Engineer}
\end{tabularx}
\end{table}
\par
\hspace{20pt}Developing and programming various systems and technologies for the construction industry. 
My work is mainly based in radio link alarm systems and turnstile controllers for access control. 
\begin{itemize}
    \item{\textbf{Technologies:} C, C++, USB, PIC24, RaspberryPi, CC112X, Linux, Cross Compiling, boost, Qt}
    \item{\textbf{Key Duties Achievements:}}
\\$\cdot$ Firmware programming of radio alarm system, turnstile controller and access control.
\\$\cdot$ Design of new radio link protocol EN54 compatible.
\\$\cdot$ Electromagnetic compatibility testing passed for EN54.
\end{itemize}

\begin{table}[H]
\begin{tabularx}{\textwidth}{lcXr}
\textbf{\href{http://www.s2e.es/en}{Solving systems engineering}} & \emph{Sevilla (August 2013 to February 2016)} & & \textbf{Embedded Systems Engineer}\\
\textbf{\href{http://aicia.es/en}{AICIA}}     & \emph{Sevilla (August 2012 to July 2013)} & & \textbf{Electronics Engineer}
\end{tabularx}
\end{table}
\par
\hspace{20pt}Developing full custom electronic systems for research purposes. 
\hspace{20pt}Developing of Electronic systems: System design, component selection, PCB design, 
manufacture of prototype, programming (both firmware and computer control) and testing. 
\begin{itemize}
    \item{\textbf{Technologies:} CAN, CANopen, I2C, UART, ADC, DAC, PWM, Ethernet, Bluetooth, C, C\#, HTML, JavaScript, PIC32, SCADA}
    \item{\textbf{Key Duties Achievements:}}
\\$\cdot$ Developed a vector impedance meter for a meat processing research project.
\\$\cdot$ Developed research projects for Abengoa successfully in time and functionality (ECOBOYA and ARESS).
\\$\cdot$ Thesis: Development of hardware battery emulator controlled by software via Ethernet and USB (150 W).
\end{itemize}

\begin{table}[H]
\begin{tabularx}{\textwidth}{lcXr}
\textbf{Freelance projects} & & & \textbf{Embedded systems developer}
\end{tabularx}
\end{table}
\par
\hspace{20pt} Design, manufacturing of prototypes and firmware development of small bespoke embedded system for various applications.
As freelance I have developed different projects from idea to product (Concept, PCB design, PCB manufacturing, firmware development) through the last years. 
\begin{itemize}
    \item{\textbf{Technologies:} C, C++ MQTT, IoT, KICAD, ESP32, ESP8266}
    \item{\textbf{Main projects:}}
\\$\cdot$ \textbf{Smart IoT bin} PCB design and manufacturing. Device developed for Mobile World Congress. Ultrasound sensor of bin load. Reports its status to operations to collect and replace bag.
\\$\cdot$ \textbf{Access control bridge} FW development. Code rework and new capabilities developed for a commercial door controller bridge (BLE to WiFi)
\\$\cdot$ \textbf{Guest house control} PCB design and outsourced manufacturing. HVAC control and noise measurement reporting for guest house renting (Airbnb, booking...)
\\$\cdot$ \textbf{People counter} PCB design. Demo board capable of counting people using WiFi join attmps from mobile phones. Connected to 3G 
\end{itemize}
\vspace{1cm}

\textbf{Education and Qualifications}\\\linea\\

\textbf{Telecommunications Engineer}\emph{ Sevilla (2008-2014), Milano (2014-2015), Sevilla (2017)}
\begin{labeling}{\hspace{20pt}}
\item{Five year engineering degree specialisation in electronics. I took the last year in Milano, Italy, as part of an international mobility programme (Erasmus programme) and presented the thesis in 2017.}
\end{labeling}

\end{document}
